The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
conclusion
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@143 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\section{Conclusion}

We have shown how RDF serializations can become very powerful
hypermedia types by using a simple vocabulary. We have argued briefly
that some triples should be added to every information resource, but
note that most triples are only relevant to write-operations and
should only appear in that case. We also noted that SPARQL is
important for non-trivial traversal of Linked Data. In summary, the
addition of the following triples would make life easier for
developers of applications that use Semantic Web data:

\begin{verbatim}
<> hm:canBe hm:mergedInto, hm:replaced , hm:deleted ;
   hm:createSimilarAt <../> ;
   hm:acceptsFormats <http://www.w3.org/ns/formats/Turtle> ;
   void:inDataset [ void:sparqlEndpoint </sparql> . ] .
\end{verbatim}
